\textsf{jaxoplanet}: Hardware-Accelerated Computation of Stellar Light Curves

### 2024-10-16 latex/paper.tex
feat: add kepler's equation solver

\subsection{Kepler's equation solver}
\todo{}
\subsection{Light curve functions and transformations}
\todo{}

>>>>

\subsection{Kepler's equation solver}
A core difference between our implementation and that of \cite{starry} and \cite{exoplanet} lies in the method used to solve Kepler's equation
\begin{equation}
    M = E - e \sin(E)
\end{equation}
Indeed, iterative methods used in previous implementations (such as \citealt{Raposo2017} and \citealt{Brandt2021}) cannot be easily implemented in \textsf{JAX} and are not extensible to GPU or TPU acceleration. Instead, our implementation makes use of \cite{Markley1995} which leads to state-of-the-art precision and runtime performance.\\\\
Although JAX features automatic differentiation, we find that explicitly implementing the derivatives of the Kepler equation solver is more efficient. To do so, we use the implicit function theorem to derive the “Jacobian-vector product” required by \textsf{JAX} to specify custom derivatives. This is done by differentiating Kepler's equation as
\begin{equation}
    \mathrm{d}M = \mathrm{d}E\,(1 - e \cos E) - \mathrm{d}e\;\sin E,
\end{equation}
which leads to
\begin{equation}
\mathrm{d}E = \frac{1}{1 - e \cos E}\;\mathrm{d}M + \frac{\sin E}{1 - e \cos E}\;\mathrm{d}e.
\end{equation}
Then, for a given value of $E$, its derivatives can be easily evaluated. We find that this method is 6 times faster than using \textsf{JAX}'s automatic differentiation\footnote{Test performed on an M2 Max Macbook.}.\\\\
\subsection{Light curve functions and transformations}
\todo{}
